Reproducible and programmatic generation of neuroimaging visualisations

### 2022-04-05 manuscript.Rmd
fig up2

---
title: "Reproducible and programmatic generation of neuroimaging visualisations"
author: "Sidhant Chopra, Löic Labache, Winnie Orchard, [...]"
date: "09/03/2022"
output:
  word_document: default
  pdf_document: default
  html_document: default
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

>>>>

---
title: "Reproducible and programmatic generation of neuroimaging visualisations"
author: "Sidhant Chopra, Löic Labache, Winnie Orchard, [...]"
date: "09/03/2022"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---
